Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-25 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more edits

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% General:
The detection of gravitational waves produced by coalescing compact binaries
allows us to explore the dynamical, nonlinear regime of general relativity
and to constrain modifications to it.
%
Some of these gravitational-wave events have sufficiently high
signal-to-noise ratio in the merger, allowing us to probe the relaxation of the remnant black
hole to its final, stationary state --- the so-called black-hole ringdown, which is
characterized by a set of quasinormal modes.
% Main question:
Can we use the ringdown to constrain deviations to general relativity,
as predicted by several of its contenders?
% What we do:
Here, we  address this question by using an inspiral-merger-ringdown waveform
model in the effective-one-body formalism, augmented with a parametrization of
the ringdown based on an expansion in the final black hole's spin.
%
We give a prescription on how to include in this waveform model the quasinormal mode frequencies
calculated on a theory-by-theory basis. In particular, we focus on theories that deviate
from general relativity by higher-order curvature corrections, namely,
Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
effective-field-theories of general relativity.
%
% Main conclusion:
We confront the resultant waveform models against the two loudest
gravitational-wave ringdown signals observed so far, notably, GW150914 and GW200129.
%
We find that while the Einstein-dilaton-Gauss-Bonnet theory cannot be
constrained with these events, we can place upper bounds on the
fundamental length-scale of cubic- ($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order
($\ell_{\rm qEFT} \leqslant 51.3$~km) effective-field-theories of general
relativity, and of dynamical Chern-Simons gravity ($\ell_{\rm dCS} \leqslant 38.7$~km).
%
The latter result is a concrete example of a theory presently unconstrained by
inspiral-only analyses which, however, can be constrained by merger-ringdown
studies with current gravitational-wave data.
%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Since the first detection of gravitational waves (GWs) from a binary black-hole (BBH) merger in 2015~\cite{LIGOScientific:2016aoc},
the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GWs signals~\cite{LIGOScientific:2021djp} from mergers
of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki,LIGOScientific:2020aai} and their mixture~\cite{LIGOScientific:2021qlt}. These results have been confirmed
by independent analyses, which have also identified a few new GW signals~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq,Nitz:2021zwj,Olsen:2022pin}.

@@

\begin{table}[t]
\begin{tabular}{c | c c}
\hline \hline
Theory & Constraint & This work \\
\hline
EdGB        & $\ell_{\rm EdGB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
dCS         & $\ell_{\rm dCS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm dCS} \leqslant 38.7$~km \\
cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km \\
\hline \hline
\end{tabular}
\caption{Summary of the upper limits, at $90\%$ credible level,
on the length-scale of the modified gravity theories under investigation.
They were obtained combining Bayesian-inference results from GW150914 and GW200129.
Current constraints on $\ell_{\rm th}$ are also listed.}
\label{tab:bound_summary}
\end{table}

@@

%
As an additional check, to verify the robustness of our constraint, we show in
Fig.~\ref{fig:corner_plot}, the final spin $\chi_{\rm f}$ and remnant mass
$M_{\rm f}$ for GW150914 for GR and dCS gravity.
%
We see that our \pSEOB~waveform model does not introduce substantial changes
to the GR estimates on these parameters, as required by the ParSpec expansion
(see discussion in Sec.~\ref{sec:review_parspec}).
%
In fact, we observed no bias on the estimation of $\Mf$ and $\chi_{\rm f}$
for all theories considered here.
%
\ab{For completness,} in Appendix~\ref{app:big_contour} we also
show how all other intrinsic parameter parameters remain unbiased.

@@

Let us now consider the quartic EFT of GR, as our final example.
%
In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR.
%
We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
%
As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_{\rm f}$ before $\varepsilon = 1/2$.
%
Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
%
\begin{equation}
    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level}\,.
\end{equation}
%
% \abcomm{Please update the paragraph below.}
In this theory, we have considered only $N_{\rm max} = 0$.
%
\ab{Indeed, we find that when adding the spin corrections and for $\ell_{\rm qEFT} \gtrsim 80$~km,
the waveforms can have a ringdown segment larger (sometimes seconds long) than the inspiral-plunge segment in the detectors frequency band, making the parameter estimation challenging.} \abcomm{The reference to 80 km comes out of the blue. Doesn't it? Why did you refer to it?}
% for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
% has some problems in English. I do not udnerstand it.}
%
To overcome this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
}
\label{fig:qEFT_exec_sum}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold.pdf}
\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 90\% credibility.
}
\label{fig:qEFT_cdf}
\end{figure}

@@

We presented an unified framework that combines the ParSpec framework
to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
%
We showed with concrete examples, how theory-specific QNM calculations of
slowly-rotating BHs in modified gravity theories can be mapped onto the
non-GR parameters of the ParSpec formalism.
%
The resulting \pSEOB~waveform model \ab{does} not bias (relative to GR) the inference of
the intrinsic binary parameters, as required by ParSpec (see, in particular, Fig.~\ref{fig:corner_plot} and
Fig.~\ref{fig:corner_plot_all} in Appendix~\ref{app:big_contour}),
%
Put together this allowed us to test four modified gravity theories (EdGB, dCS,
cubic, and quartic EFTs of GR) using observational data from the LVK events
GW150914 and GW200129. \ab{Our results are summarzied in Table~\ref{tab:bound_summary}.}

\ab{In particular,} we found, that within the interpretation \ab{of} these theories as EFTs and the
region of validity of the ParSpec framework, the \sout{coupling constant} \ab{fundamental length-scale} of dCS gravity is bound as
$\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
of GW150914 and GW200129. This is the first GW-alone constrain on this theory.
%
In contrast, we could not place any bounds on the \sout{coupling constant} \ab{length-scale} \abcomm{Maybe
this is common in the literature, but I would call it length-scale instead of coupling
constant. What do you think?} of EdGB gravity $\ell_{\rm EdGB}$.
%
This dichotomy between the two theories has a counterpart with works that considered
the inspiral part of the GW signal alone~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
\ab{Using data of the LVK BBHs, it was found that the posterior distributions for
deviations from GR were uninformative in dCS gravity, but not in EdGB gravity.}
We emphasize that both those theories (and the cubic EFT of GR also studied here) all predict the same exponent $p$ in ParSpec.
%
Hence, our results show how the inclusion of theory-specific information into the ParSpec framework
can result in different outcomes for different theories, even if they predict the same value of $p$.

@@

\sout{Our work shows that, with the GW signals so far observed by the LVK Collaboration,
there are theories of gravity (such as dCS) that can be unconstrained by studying the
inspiral portion of GW events, {\it yet} {it} can be constrained, if we analyze the ringdown.}
%
\sout{Our results show that to fulfill the potential to test GR with \ab{future} GW observations,
further work \ab{is needed} on modeling \sout{of} the late-inspiral-(plunge)-merger and ringdown of
coalescing BHs  (with NR simulations) and, complementary,}
%
\sout{We hope that our results can also serve as further motivation to address these
outstanding problems.}

@@

We start by considering EdGB gravity and focus on
Refs.~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} to determine the ParSpec coefficients for this theory.
% and~\cite{Pierini:2021jxd} for the QNMs of for which the QNMs of nonrotating and
% slowly-rotating BHs where calculated in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk}
% and~\cite{Pierini:2021jxd}, respectively.
%
In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
of the \hs{dominant axial gravitational-led} mode increases as the coupling constant
$\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
polar-branch of QNMs was studied in Ref.~\cite{Pierini:2021jxd}.
%
Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
\hs{we select the axial-parity branch of QNMs.}

@@

The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
which for consistency with our previous discussion, we truncate at \hs{leading-order in} $\gamma_{\rm EdGB}$
% \abcomm{$\ell_{\rm EdCS}^4$?}.
%
\hs{We can expand the resulting formula} in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
and re-expand in small coupling and spin.
%
These steps yield \ab{for} $p_{\rm EdGB} = 4$,
%
\begin{align}
     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
\end{align}
%
for the $j=0$ coefficients and
%
\begin{equation}
    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
\end{equation}
%
for the $j=1$ coefficients.

@@

% HS: I agree with all the changes below
We show in Fig.~\ref{fig:corner_plot_all} a corner plot for all the intrinsic
binary parameters from our parameter-estimation study of GW150914, using the
\pSEOB{} waveform models for GR and dCS.
%
We see that the medians of the posterior distributions are not affected substantially by the inclusion of the non-GR parameters.
%
This is particularly important for the $\Mf$ and $\chi_{\rm f}$ parameters, since
the ParSpec framework assumes that the non-GR theory induces small deviations from GR.
%
We obtain qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
%
We also remark that the fact that the posterior on $\chi_{\rm f}$ has most support around $\approx 0.7$ justifies our use
of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
% General:
The detection of gravitational waves produced by coalescing compact binaries
allows us to explore the dynamical, nonlinear regime of general relativity
and to constrain modifications to it.
%
Some of these gravitational-wave events have sufficiently high
signal-to-noise ratio in the merger, allowing us to probe the relaxation of the remnant black
hole to its final, stationary state --- the so-called black-hole ringdown, which is
characterized by a set of quasinormal modes.
% Main question:
Can we use the ringdown to constrain deviations to general relativity,
as predicted by several of its contenders?
% What we do:
Here, we  address this question by using an inspiral-merger-ringdown waveform
model in the effective-one-body formalism, augmented with a parametrization of
the ringdown based on an expansion in the final black hole's spin.
%
We give a prescription on how to include in this waveform model the quasinormal mode frequencies
calculated on a theory-by-theory basis. In particular, we focus on theories that modify
general relativity by higher-order curvature corrections, namely,
Einstein-dilaton-Gauss-Bonnet, dynamical Chern-Simons, cubic- and quartic-order
effective-field-theories of general relativity.
%
% Main conclusion:
We confront the resultant waveform models against the two loudest
gravitational-wave ringdown signals observed so far, notably, GW150914 and GW200129.
%
We find that while the Einstein-dilaton-Gauss-Bonnet theory cannot be
constrained with these events, we can place upper bounds on the
fundamental length-scale of cubic- ($\ell_{\rm cEFT} \leqslant 38.2$~km) and quartic-order
($\ell_{\rm qEFT} \leqslant 51.3$~km) effective-field-theories of general
relativity, and of dynamical Chern-Simons gravity ($\ell_{\rm dCS} \leqslant 38.7$~km).
%
The latter result is a concrete example of a theory presently unconstrained by
inspiral-only analyses which, however, can be constrained by merger-ringdown
studies with current gravitational-wave data.
%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%

@@

Since the first detection of gravitational waves (GWs) from a binary black-hole (BBH) merger in 2015~\cite{LIGOScientific:2016aoc},
the LIGO~\cite{LIGOScientific:2014pky} and Virgo~\cite{VIRGO:2014yos} detectors have observed about 90 GW events~\cite{LIGOScientific:2021djp} from mergers
of BHs, neutron stars (NSs) \cite{TheLIGOScientific:2017qsa,LIGOScientific:2018cki,LIGOScientific:2020aai} and their mixture~\cite{LIGOScientific:2021qlt}. These results have been confirmed
by independent analyses, which have also identified a few new GW signals~\cite{Nitz:2018imz,Nitz:2019hdf,Venumadhav:2019lyq,Zackay:2019btq,Nitz:2021zwj,Olsen:2022pin}.

@@

\begin{table}[t]
\begin{tabular}{c | c c}
\hline \hline
Theory & Constraint & This work \\
\hline
EdGB        & $\ell_{\rm EdGB} \leqslant 1.18$~km~(GW)~\cite{Lyu:2022gdr} & -- \\
dCS         & $\ell_{\rm dCS} \leqslant 8.5$~km~(EM+GW)~\cite{Silva:2020acr}  & $\ell_{\rm dCS} \leqslant 38.7$~km \\
cubic EFT   & -- & $\ell_{\rm cEFT} \leqslant 38.2$~km \\
quartic EFT & $\ell_{\rm qEFT} \leqslant 150$~km~\cite{Sennett:2019bpc}  & $\ell_{\rm qEFT} \leqslant 51.3$~km\hs{$^{\ast}$} \\
\hline \hline
\end{tabular}
\caption{Summary of the upper limits, at $90\%$ credible level,
on the length-scale of the modified gravity theories under investigation.
They were obtained combining Bayesian-inference results from GW150914 and GW200129.
Current constraints on $\ell_{\rm th}$ are also listed.
%
\hs{Our result for the quartic EFT of GR is only in marginal tension with our hard cut-off scale for the
validity of the theory and hence we do still quote it here. See Sec.~\ref{sec:results_qeft} for details.}
}
\label{tab:bound_summary}
\end{table}

@@

%
As an additional check, to verify the robustness of our constraint, we show in
Fig.~\ref{fig:corner_plot}, the final spin $\chi_{\rm f}$ and remnant mass
$M_{\rm f}$ for GW150914 for GR and dCS gravity.
%
We see that our \pSEOB~waveform model does not introduce substantial changes
to the GR estimates on these parameters, as required by the ParSpec expansion
(see discussion in Sec.~\ref{sec:review_parspec}).
%
In fact, we observed no bias on the estimation of $\Mf$ and $\chi_{\rm f}$
for all theories considered here.
%
For completness, in Appendix~\ref{app:big_contour} we also
show how all other intrinsic parameter parameters remain unbiased.

@@

Let us now consider the quartic EFT of GR, as our final example.
%
In Fig.~\ref{fig:qEFT_exec_sum} we show the posteriors on $\ell_{\rm qEFT}$ for GW150914 (top panel),
GW200129 (middle panel) for $N_{\rm max} = 0$, which are qualitatively similar to the cubic EFT of GR.
%
We find that both the EFT~\eqref{eq:eft_bound} and ParSpec~\eqref{eq:parspec_bound} are satisfied,
hence allowing us to infer bounds on $\ell_{\rm qEFT}$.
%
As Fig.~\ref{fig:qEFT_cdf} shows the CDFs for both events reach 90\% for $\gm = M_{\rm f}$ before $\varepsilon = 1/2$.
%
Consequently, from the joint posterior of $\ell_{\rm qEFT}$ we quote our final result,
%
\begin{equation}
    \ell_{\rm qEFT} \leqslant 51.3~\textrm{km} \quad \textrm{at 90\% credible level}\,.
\end{equation}
%
% \abcomm{Please update the paragraph below.}
In this theory, we have considered only $N_{\rm max} = 0$.
%
\ab{Indeed, we find that when adding the spin corrections and for $\ell_{\rm qEFT} \gtrsim 80$~km,
the waveforms can have a ringdown segment larger (sometimes seconds long) than the inspiral-plunge segment in the detectors frequency band, making the parameter estimation challenging.} \abcomm{The reference to 80 km comes out of the blue. Doesn't it? Why did you refer to it?}
% for which the ringdown portions of the larger than the inspiral-plunge part. \abcomm{The last sentence
% has some problems in English. I do not udnerstand it.}
%
To overcome this issue we have lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we have obtained posteriors
which were flat, just as our prior, and were thus uninformative. Hence, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/qeft_posteriors_combined_corrected.pdf}
\caption{(Color online).~Posterior distribution function for the coupling constant $\ell_{\rm qEFT}$ for
GW150914 (top panel), GW200129 (middle panel) and combined events (bottom panel).
}
\label{fig:qEFT_exec_sum}
\end{figure}

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/qeft_cdf_varying_threshold_corrected.pdf}
\caption{Similar to Fig.~\ref{fig:edgb_cdf}, but for the quartic EFT of GR.
We find that similarly to what happens in dCS gravity and the cubic EFT of GR, we
can place a constrain on $\ell_{\rm qEFT}$ when $\gm = M_{\rm f}$ for both events at 90\% credibility.
}
\label{fig:qEFT_cdf}
\end{figure}

@@

We presented an unified framework that combines the ParSpec framework
to model deviations to the GR QNMs~\cite{Maselli:2019mjd} with the \pSEOB~waveform model~\cite{Brito:2018rfr,Ghosh:2021mrv}.
%
We showed with concrete examples, how theory-specific QNM calculations of
slowly-rotating BHs in modified gravity theories can be mapped onto the
non-GR parameters of the ParSpec formalism.
%
The resulting \pSEOB~waveform model \ab{does} not bias (relative to GR) the inference of
the intrinsic binary parameters, as required by ParSpec (see, in particular, Fig.~\ref{fig:corner_plot} and
Fig.~\ref{fig:corner_plot_all} in Appendix~\ref{app:big_contour}),
%
Put together this allowed us to test four modified gravity theories (EdGB, dCS,
cubic, and quartic EFTs of GR) using observational data from the LVK events
GW150914 and GW200129. Our results are summarized in Table~\ref{tab:bound_summary}.

In particular, we found, that within the interpretation of these theories as EFTs and the
region of validity of the ParSpec framework, the fundamental length-scale of dCS gravity is bound as
$\ell_{\rm dCS} \leqslant 34.5$~km, at 90\% credible level, when stacking the posteriors
of GW150914 and GW200129. This is the first GW-alone constrain on this theory.
%
In contrast, we could not place any bounds on the \hs{fundamental} length-scale \abcomm{Maybe
this is common in the literature, but I would call it length-scale instead of coupling
constant. What do you think?}~\hscomm{I agree.} of EdGB gravity $\ell_{\rm EdGB}$.
%
This dichotomy between the two theories has a counterpart with works that considered
the inspiral part of the GW signal alone~\cite{Nair:2019iur,Perkins:2021mhb,Lyu:2022gdr}.
%
Using data of the LVK BBHs, it was found that the posterior distributions for
deviations from GR were uninformative in dCS gravity, but not in EdGB gravity.
We emphasize that both those theories (and the cubic EFT of GR also studied here) all predict the same exponent $p$ in ParSpec.
%
Hence, our results show how the inclusion of theory-specific information into the ParSpec framework
can result in different outcomes for different theories, even if they predict the same value of $p$.

@@

% \sout{Our work shows that, with the GW signals so far observed by the LVK Collaboration,
% there are theories of gravity (such as dCS) that can be unconstrained by studying the
% inspiral portion of GW events, {\it yet} {it} can be constrained, if we analyze the ringdown.}
% %
% \sout{Our results show that to fulfill the potential to test GR with \ab{future} GW observations,
% further work \ab{is needed} on modeling \sout{of} the late-inspiral-(plunge)-merger and ringdown of
% coalescing BHs  (with NR simulations) and, complementary,}
% %
% \sout{We hope that our results can also serve as further motivation to address these
% outstanding problems.}

@@

We start by considering EdGB gravity and focus on
Refs.~\cite{Blazquez-Salcedo:2016enn,Pierini:2021jxd} to determine the ParSpec coefficients for this theory.
% and~\cite{Pierini:2021jxd} for the QNMs of for which the QNMs of nonrotating and
% slowly-rotating BHs where calculated in Refs.~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk}
% and~\cite{Pierini:2021jxd}, respectively.
%
In particular, Ref.~\cite{Blazquez-Salcedo:2016enn} found that the damping time
of the \hs{dominant \emph{axial} gravitational-led} mode increases as the coupling constant
$\ell_{\rm EdGB}$ is increased. The leading-order spin corrections to the
\emph{polar}-parity QNMs was studied in Ref.~\cite{Pierini:2021jxd}.
%
Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
\hs{we select the axial-parity branch of QNMs and
%
for consistency, we only consider the leading-order $j=0$ coefficients in EdGB gravity.}

@@

\hscomm{There was an error here: I mixed the axial QNMs we used for the nonrotating coefficients, with the polar QNMs
for which the spin-corrections were computed. Because it is inconsistent, I suggest changing opening paragraph with the highlighted text,
and then remove the $N_{\rm max} = 1$ results from our EdGB plots. What do you think?}
%
The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
which for consistency with our previous discussion, we truncate at \hs{leading-order in} $\gamma_{\rm EdGB}$
% \abcomm{$\ell_{\rm EdCS}^4$?}.

\hscomm{Could remove this part until the end of this section.}
\hs{We can expand the resulting formula} in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$ can be
read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
and re-expand in small coupling and spin.
%
These steps yield \ab{for} $p_{\rm EdGB} = 4$,
%
\begin{align}
     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
\end{align}
%
for the $j=0$ coefficients and
%
\begin{equation}
    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
\end{equation}
%
for the $j=1$ coefficients.

@@

% HS: I agree with all the changes below
We show in Fig.~\ref{fig:corner_plot_all} a corner plot for all the intrinsic
binary parameters from our parameter-estimation study of GW150914, using the
\pSEOB{} waveform models for GR and dCS.
%
We see that the medians of the posterior distributions are not affected substantially by the inclusion of the non-GR parameters.
%
This is particularly important for the $\Mf$ and $\chi_{\rm f}$ parameters, since
the ParSpec framework assumes that the non-GR theory induces small deviations from GR.
%
We obtain qualitative similar results for GW200129 and the other modified gravity theories considered in our work.
%
We also remark that the fact that the posterior on $\chi_{\rm f}$ has most support around $\approx 0.7$ justifies our use
of the fitting coefficients in the ParSpec formulas of Ref.~\cite{Maselli:2019mjd}.
%
\hscomm{Should we say that this happens almost by ``construction''? That would be because \pSEOB{} waveform changes very little the inspiral
and the final masses and spins are predicted according to a GR formula.}
